Limited plasticity but increased variance in physiological rates across ectotherm populations under climate change

### 2024-07-14 ms.qmd
delet spaces

        # Contrasts for pooled acute and acclimation across life stage categories. Checked freshwater and looks correct.
            contrast_lnvr_lh_cat_stats <- rbind(get_lifestage(pred_lh_vr, habitat = "t", lh_b_data),
                                                get_lifestage(pred_lh_vr, habitat = "m", lh_b_data),
                                                get_lifestage(pred_lh_vr, habitat = "f", lh_b_data))
```

>>>>

        # Contrasts for pooled acute and acclimation across life stage categories. Checked freshwater and looks correct.
            contrast_lnvr_lh_cat_stats <- rbind(get_lifestage(pred_lh_vr, habitat = "t", lh_b_data),
                                                get_lifestage(pred_lh_vr, habitat = "m", lh_b_data),
                                                get_lifestage(pred_lh_vr, habitat = "f", lh_b_data))
